Changing Flights In The Air\\ (Abortable Chain Agreement)

### 2015-05-09 paper/paper.tex
Work on the abstract

\abstract{
    To achieve consistent performance, a distributed computing service must
    dynamically adapt to unpredictable crashes, communication failures, and
    changes in the availability of shared resources.
    Unfortunately, most existing algorithms are not adaptive: outside of their
    sweet spot, they have poor performance.

>>>>

\input{abstract2}
